Hydra Battles and Cie

### 2021-07-11 doc/part-hydras.tex
fix a naming inconsistency

\begin{Coqsrc}
Lemma H'_omega_sqr : forall k,
    H'_ (Phi0  2)%e0 k = (exp2 (S k ) * (S k) - 1)%nat.
Proof.
  intro k; rewrite H'_eq3; auto with E0.
  - ochange (Canon (Phi0 2) (S k)) (omega * (S k))%e0.
    +  rewrite H'_omega_i; simpl (exp2 (S k)).
       *  rewrite Nat.add_pred_r.
          -- abstract lia. 
          -- generalize (exp2_not_zero k); abstract lia.
    + cbn; f_equal; abstract lia.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_Omega_term_1 : alpha <> Zero -> forall k,  
    H'_ (Omega_term alpha (S i)) k =
    H'_ (Omega_term alpha i) (H'_ (Phi0 alpha) k).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_Omega_term (alpha : E0):
alpha <> Zero -> forall i k, 
  H'_ (Omega_term alpha i) k = iterate (H'_ (Phi0 alpha)) (S i) k.
\end{Coqsrc}

@@

Lemma H'_Phi0_succ alpha  : alpha <> Zero -> forall k,
 H'_ (Phi0 (Succ alpha)) k = H'_succ_fun (H'_ (Phi0 alpha)) k.

Lemma H'_Phi0_Si : forall i k,
 H'_ (Phi0 (S i)) k = iterate H'_succ_fun i (H'_ omega) k. 
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_omega_cube : forall k,
    H'_ (Phi0 3)%e0 k = iterate (H'_ (Phi0 2))  (S k) k.
Proof.
  intro k; rewrite <-FinS_eq, -> Fin_Succ, H'_Phi0_succ; auto.
  compute; injection 1; discriminate.
Qed.
\end{Coqsrc}

@@

Remark R0 k :  H'_ (Phi0 3)%e0 k = iterate f (S k) k.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fact F0 : H'_ (Phi0 3) 3 = f (f (f (f 3))).
proof. rewrite R0; reflexivity. Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fact F1 : H'_ (Phi0 3) 3 = f (f N).
Proof.
 rewrite F0; reflexivity. 
Qed.

Lemma F1_simpl : H'_ (Phi0 3) 3 =
                 (exp2 (exp2 (S N) * S N) * (exp2 (S N) * S N) - 1)%nat.

@@

\begin{Coqsrc}
Lemma H'_Phi0_omega : forall k, H'_ (Phi0 omega) k =
                               iterate H'_succ_fun  k (H'_ omega) k.
Proof with auto with E0.
  intro k; rewrite H'_eq3, <- H'_Phi0_Si ...
  -  rewrite CanonS_Canon, CanonS_Phi0_lim;  f_equal ...
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_Phi0_omega_closed_formula k :
  H'_ (Phi0 omega) k =
  iterate (fun (f: nat -> nat) (l : nat) => iterate  f (S l) l)
               k
               (fun k : nat => S (2 * k)%nat)
               k.
\end{Coqsrc}

>>>>

\begin{Coqsrc}
Lemma H'_omega_sqr : forall k,
    H'_ (phi0  2)%e0 k = (exp2 (S k ) * (S k) - 1)%nat.
Proof.
  intro k; rewrite H'_eq3; auto with E0.
  - ochange (Canon (phi0 2) (S k)) (omega * (S k))%e0.
    +  rewrite H'_omega_i; simpl (exp2 (S k)).
       *  rewrite Nat.add_pred_r.
          -- abstract lia. 
          -- generalize (exp2_not_zero k); abstract lia.
    + cbn; f_equal; abstract lia.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_Omega_term_1 : alpha <> Zero -> forall k,  
    H'_ (Omega_term alpha (S i)) k =
    H'_ (Omega_term alpha i) (H'_ (phi0 alpha) k).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_Omega_term (alpha : E0):
alpha <> Zero -> forall i k, 
  H'_ (Omega_term alpha i) k = iterate (H'_ (phi0 alpha)) (S i) k.
\end{Coqsrc}

@@

Lemma H'_phi0_succ alpha  : alpha <> Zero -> forall k,
 H'_ (phi0 (Succ alpha)) k = H'_succ_fun (H'_ (phi0 alpha)) k.

Lemma H'_phi0_Si : forall i k,
 H'_ (phi0 (S i)) k = iterate H'_succ_fun i (H'_ omega) k. 
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_omega_cube : forall k,
    H'_ (phi0 3)%e0 k = iterate (H'_ (phi0 2))  (S k) k.
Proof.
  intro k; rewrite <-FinS_eq, -> Fin_Succ, H'_phi0_succ; auto.
  compute; injection 1; discriminate.
Qed.
\end{Coqsrc}

@@

Remark R0 k :  H'_ (phi0 3)%e0 k = iterate f (S k) k.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fact F0 : H'_ (phi0 3) 3 = f (f (f (f 3))).
proof. rewrite R0; reflexivity. Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fact F1 : H'_ (phi0 3) 3 = f (f N).
Proof.
 rewrite F0; reflexivity. 
Qed.

Lemma F1_simpl : H'_ (phi0 3) 3 =
                 (exp2 (exp2 (S N) * S N) * (exp2 (S N) * S N) - 1)%nat.

@@

\begin{Coqsrc}
Lemma H'_phi0_omega : forall k, H'_ (phi0 omega) k =
                               iterate H'_succ_fun  k (H'_ omega) k.
Proof with auto with E0.
  intro k; rewrite H'_eq3, <- H'_phi0_Si ...
  -  rewrite CanonS_Canon, CanonS_phi0_lim;  f_equal ...
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma H'_phi0_omega_closed_formula k :
  H'_ (phi0 omega) k =
  iterate (fun (f: nat -> nat) (l : nat) => iterate  f (S l) l)
               k
               (fun k : nat => S (2 * k)%nat)
               k.
\end{Coqsrc}
